Propaganda Films and National Identity: Animated Films in USSR and China

### 2025-03-16 drafts/40319a1230e9df6e4200433c4260983e88921b60.qmd
finalize paper

![The kids standing on the street](fig/shui1.png){#fig-shuib}

@@

Yu Tong [-@wanYuTong1959] in 1959 employs the paper cutout animation invented by the director Wan Guchan, one of the pioneering Wan brothers who revolutionized the Chinese animation industry. This method combines traditional Chinese shadow play and paper cutting with animation techniques. Characters in Yu Tong are follow a distinct Chinese aesthetic. As shown in @fig-yuto1a, The protagonist, Yu Tong, is portrayed as a classical Chinese children with big eyes, thick eyebrows, arms and legs like lotus root, and black hair. The other protagonists include a missionary from the West dressed in black and an old fisherman as a peasant, as shown in @fig-yuto1c. The background of the film specially reflect the traditional Chinese art with a mixture of Japanese influence, like @fig-yuto1b, and the music in background is played with traditional Chinese instruments. Based on the overall theme of the film, it is targeting children.

::: {#fig-yuto1 layout-ncol=3}

![Main characters of the film](fig/yuto6.png){#fig-yuto1a}

![Style of background](fig/yuto1.png){#fig-yuto1b}

![Other main protagonists](fig/yuto2.png){#fig-yuto1c}

Stills from Yu Tong
:::

Recurring motifs including lotus and Chinese ware reinforce the film's themes and cultural context of traditional Chinese art.

>>>>

![The kids standing near a pole on the street](fig/shui1.png){#fig-shuib}

@@
